---
title: "hw05-Minjeong-Jeong"
author: "Minjeong Jeong"
date: "2018/ 4/25"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,error = TRUE,fig.path = 'image/')
```
```{r}
library(dieroller)
```


#1) Object "die"
```{r}
fair_die <- die()
fair_die
# die with non-standard sides
weird_die <- die(sides = c('i', 'ii', 'iii', 'iv', 'v', 'vi'))
weird_die
# create a loaded die
loaded_die <- die(prob = c(0.075, 0.1, 0.125, 0.15, 0.20, 0.35))
loaded_die
# bad sides
bad_die <- die(sides = c('a', 'b', 'c', 'd', 'e'))
```
#2) Object "roll"
```{r}
# roll fair die 50 times
fair_die <- die()
# roll 50 times
set.seed(123)
fair_50rolls <- roll(fair_die, times = 50)
# print
fair_50rolls
# what's in fair50?
names(fair_50rolls)
fair_50rolls$rolls
fair_50rolls$sides
fair_50rolls$prob
fair_50rolls$total
```

#3) Summary method for "roll" objects
```{r}
set.seed(123)
fair_50rolls <- roll(fair_die, times = 50)
fair50_sum <- summary(fair_50rolls)
fair50_sum
# what's in the summary
class(fair50_sum)
names(fair50_sum)
fair50_sum$freqs
```

#4) Plot methd for "roll" objects
```{r}
# plot method
plot(fair_50rolls)
```

#5) Additional Methods
```{r}
# roll fair die
set.seed(123)
fair_die <- die()
fair500 <- roll(fair_die, times = 500)
# summary method
summary(fair500)
# extracting roll in position 500
fair500[500]
# replacing last roll
fair500[500] <- 1
fair500[500]
summary(fair500)
# adding 100 rolls
fair600 <- fair500 + 100
summary(fair600)
# plot method
plot(fair500)
```

#De Mere's problem
##Problem 1
The first part of the problem involves computing the probability of getting at least one "6" in four rolls of die.
```{r}
library(dieroller)

set.seed(123)
series <- 0
for (i in 1:1000) {
  if(sum((roll(die(), times = 4)$rolls) == 6) != 0) {
    series  <- 1+series 
  }
}
series /1000

1-(5/6)^4
```

##Problem 2
The other problem involves computing the probability of getting at least two
“6” in 24 rolls of a pair of dice. This probability can be computed analytically as:
```{r}
set.seed(123)

series2 <- 0
for (i in 1:1000) {
  for (i in 1:24) {
    if((sum(roll(die(), times = 2)$rolls) == 12)) {
      series2 <- series2 + 1
      break
    }
  }
}

series2/1000

1-(35/36)^24
```

